---
title: "Creating Graphs with ggplot2"
author: "KKC"
date: "1/27/2020"
output: html_document
---

# Plots with ggplots2

We are going to make plots in R using the gglots2 package from the tidyverse

We will install these packages:

-tidyverse
-readxl
-here

```{r setup, message=FALSE}
library(tidyverse) #install.packages("tidyverse")
library(readxl)  #install.packages("readxl")
library(here)  #install.packages("here")

```

#California National Parks Data

```{r read-data}

ca_np <- read_csv(here("data/ca_np.csv"))

ci_np <- read_excel(here("data", "ci_np.xlsx"))

```

## Make my own first graph!!

We're going to make a line plot of year that will be X variable and Visitors that will be y variable in ggplot:

Ctrl + Alt + I
```{r}
ggplot(data = ci_np, aes(x = year, y = visitors))  + 
  geom_line()


```

Making a base layer for my CI plots
```{r}
gg_base <- ggplot(data = ci_np, aes(x = year, y = visitors))


```

### Now let's start customizing!

- Line / point colors: color
- Change line type: linetype
- Change point style: pch
- Change transparency: alpha

```{r}
gg_base + 
  geom_line(
    color = "purple",
    linetype = "dashed"
  )



```
```{r}
gg_base + 
  geom_point(
    color = "black",
    pch = 2,
    size = 3
    
  )
```

### Update graph aesthetics based on variables

```{r}
gg_base +
  geom_point(
    aes(size = visitors,
        color = year)
  )
```

###  Use gg-themes for overall updates

- theme_light()
- theme_minimal()
- theme_bw()
```{r}
gg_base +
  geom_area() +
  theme_bw()


```
### Create a multi-series line plot using data for all CA National Parks

```{r}
ggplot(data = ca_np, aes(x = year, y = visitors, group = park_name)) +
  geom_line( aes(color = park_name))
```

```{r}
my_np_graph <-ggplot (data = ca_np, aes(x = year, y = visitors)) + 
  geom_point(aes(color = park_name)) +
  facet_wrap(~park_name, scales = "free") +
  theme_minimal()
```
Export my graph as a .png
```{r}
ggsave(plot = my_np_graph, here("figures", "np_graph.png"))
```


